\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-07 poster.tex
poster acknowledgments
single character

\begin{block}{Ongoing work: Generative models}
  Learn probabilistic program (a regex) $p_n$ from $K$ strings $x_n = \left\{y_n^k \right\}_{k = 1}^k$.

@@

>>>>

\begin{block}{Ongoing work: Generative models}
  Learn probabilistic program (a regex) $p_n$ from $K$ strings $x_n = \left\{y_n^k \right\}_{k = 1}^K$.

@@

\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

\begin{block}{Acknowledgements}

  We gratefully acknowledge collaboration with Eyal Dechter, whose EC algorithm (Dechter et al, IJCAI 2013) provided the inspiration for DreamCoder, and Luke Hewitt, who graciously provided us with
  a regex learning data set.
